### 2020-06-05 6_related.tex
edit figures and indent to bring the paper back to 11 pages
Un-itemize the bulleted lists in sections 7 and 8.

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. {\color{blue} The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models.} In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:

@@

\begin{itemize}

\item
The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.

\item
One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.

\item
A report on the Mantevo project~\cite{Mantevo09} describes a number of
mini-apps, but only includes self-comparisons based on reference
implementations.

\item
A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, and of those three only two can be compared in an
apples-to-apples manner as the last implementation uses a structured
rather than an unstructured mesh. A follow-up paper describes another
implementation in Regent~\cite{Regent15} (comparison against reference
only).

\end{itemize}

Microbenchmarks can be easier to implement, but do not solve the
asymptotic costs of implementation. PRK Stencil~\cite{PRK14} contains a
2D stencil and is evaluated on implementations in MPI, SHMEM, UPC,
Charm++, and Grappa~\cite{PRKRuntimes16}. The NAS benchmark
suite~\cite{NAS91, NAS95} consists mostly of small kernels for dense
or sparse matrix computations and has implementations in
OpenMP~\cite{NASOpenMP99}, MPI and MPI+OpenMP~\cite{NASMPIOpenMP00},
and Charm++~\cite{NASCharm96}. PRK requires $\mathcal{O}(n)$ effort to
implement (for $n$ systems) by virtue of being only a single
computational pattern, while NAS requires $\mathcal{O}(mn)$ overall
effort (for $m$ patterns and $n$ systems). In contrast, Task Bench
requires $\mathcal{O}(m+n)$ effort and is easily extended to cover new
systems or patterns with $\mathcal{O}(1)$ effort for each additional
system or pattern.

>>>>

@@

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. {\color{blue} The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models.} In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:
(a) The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.
(b) One follow-up paper for the mini-app CoMD describes a Chapel
implementation~\cite{CoMDChapel16} (comparison against reference
only). Additional follow-up papers consider aspects of the reference
implementation only~\cite{CoMDLoadImbalance17,
  CoMDThreadedModels14}.
(c) A report on the Mantevo project~\cite{Mantevo09} describes a number of
mini-apps, but only includes self-comparisons based on reference
implementations.
And (d) A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, and of those three only two can be compared in an
apples-to-apples manner as the last implementation uses a structured
rather than an unstructured mesh. A follow-up paper describes another
implementation in Regent~\cite{Regent15} (comparison against reference
only).

Microbenchmarks can be easier to implement, but do not address the
asymptotic costs of implementation. PRK Stencil~\cite{PRK14} contains a
2D stencil and is evaluated on implementations in MPI, SHMEM, UPC,
Charm++, and Grappa~\cite{PRKRuntimes16}. The NAS benchmark
suite~\cite{NAS91, NAS95} consists mostly of small kernels for dense
or sparse matrix computations and has implementations in
OpenMP~\cite{NASOpenMP99}, MPI and MPI+OpenMP~\cite{NASMPIOpenMP00},
and Charm++~\cite{NASCharm96}. PRK requires $\mathcal{O}(n)$ effort to
implement (for $n$ systems) by virtue of being only a single
computational pattern, while NAS requires $\mathcal{O}(mn)$ overall
effort (for $m$ patterns and $n$ systems). In contrast, Task Bench
requires $\mathcal{O}(m+n)$ effort and is easily extended to cover new
systems or patterns with $\mathcal{O}(1)$ effort for each additional
system or pattern.
